---
title: "Report"
author: "Xiru Lyu,Tiffany Cheng"
date: "2/13/2018"
output: pdf_document
---

```{r,include=FALSE}
source('Graph.R') # attach the R script that contains major 
```

## Background

## Comparison of 2010 and 2017 Data by Month

Figure 1 and 2 show the comparison of total number of illeagl alien apprehensions in 2010 and 2017 by month. The total number of apprehensions is generally lowerer in 2017 compared with data in 2010 for each month. There was a sharp decrease in the number of total apprehensions in Tucson from 2010 to 2017. However, it's noteworthy to point out that there was a large increase in the total number of apprehension in Rio Grande Valley from 2010 to 2017.

```{r month plot,echo=FALSE,fig.align='center',fig.cap='Comparison of Data by Month',fig.height=8}
par(mfrow=c(3,2))
month_graph(PB2010,PB2017,'October')
month_graph(PB2010,PB2017,'November')
month_graph(PB2010,PB2017,'December')
month_graph(PB2010,PB2017,'January')
month_graph(PB2010,PB2017,'Feburary')
month_graph(PB2010,PB2017,'March')
month_graph(PB2010,PB2017,'April')
month_graph(PB2010,PB2017,'May')
month_graph(PB2010,PB2017,'June')
month_graph(PB2010,PB2017,'July')
month_graph(PB2010,PB2017,'August')
month_graph(PB2010,PB2017,'September')
```


# Comparison of 2010 and 2017 Data by Sector

Figure 3 and 4 show the comparsion of total number of illegal alien apprehensions in 2010 and 2017 by sector. In some sectors such as El Centro, San Diego, and Tucson, there was a significant drop in total number of apprehensions for each month from 2010 to 2017. In contrast, the total number of apprehensions increased sharply in every month in sectors such as El Paso, Rio Grande Valley, andYuma from 2010 to 2017.

```{r sector plot,echo=FALSE,fig.align='center',fig.cap='Comparison of Data by Sector',fig.height=8}
par(mfrow=c(3,2))
sector_graph(PB2010,PB2017,'Big Bend')
sector_graph(PB2010,PB2017,'Del Rio')
sector_graph(PB2010,PB2017,'El Centro')
sector_graph(PB2010,PB2017,'El Paso')
sector_graph(PB2010,PB2017,'Laredo')
sector_graph(PB2010,PB2017,'Rio Grande Valley')
sector_graph(PB2010,PB2017,'San Diego')
sector_graph(PB2010,PB2017,'Tucson')
sector_graph(PB2010,PB2017,'Yuma')
```

