---
title: "Analysis of Trends in Apprehensions Along the United States Southern Border"
author: "Xiru Lyu and Tiffany Cheng"
date: "2/19/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source('Basic.R')
```

## Background

Illegal crossing of the United States southern border has been a central topic of debate in the current political climate. The data are from the US Customs and Border Protection. It is of particular interest to note that the federal fiscal year 2017 saw a all-time low in apprehensions compared to the past 17 years.

## Comparision of Each Sector by Month

```{r}
par(mfrow=c(3,4))
month_graph(PB2010,PB2017,'October')
month_graph(PB2010,PB2017,'November')
month_graph(PB2010,PB2017,'December')
month_graph(PB2010,PB2017,'January')
month_graph(PB2010,PB2017,'Feburary')
month_graph(PB2010,PB2017,'March')
month_graph(PB2010,PB2017,'April')
month_graph(PB2010,PB2017,'May')
month_graph(PB2010,PB2017,'June')
month_graph(PB2010,PB2017,'July')
month_graph(PB2010,PB2017,'August')
month_graph(PB2010,PB2017,'September')
```

## Comparision of Each Month by Sector

```{r}
par(mfrow=c(3,3))
sector_graph(PB2010,PB2017,'Big Bend')
sector_graph(PB2010,PB2017,'Del Rio')
sector_graph(PB2010,PB2017,'El Centro')
sector_graph(PB2010,PB2017,'El Paso')
sector_graph(PB2010,PB2017,'Laredo')
sector_graph(PB2010,PB2017,'Rio Grande Valley')
sector_graph(PB2010,PB2017,'San Diego')
sector_graph(PB2010,PB2017,'Tucson')
sector_graph(PB2010,PB2017,'Yuma')
```

## Statistical Tests: Variance Test for One-month Period {.smaller}
$$H_0: \sigma^2_{`r most_2010_s`} = \sigma^2_{`r most_2017_s`}$$ $$H_A: \sigma^2_{`r most_2010_s`} \neq \sigma^2_{`r most_2017_s`}$$

```{r}
var.test(most[,1],most[,2])
```

We fail to reject the null hypothesis at $\alpha=0.05$ and conclude that the variances of `r most_2010_s` and `r most_2017_s` are equal.

## Statistical Tests: Two Sample t-test for One-month Period {.smaller}
$$H_0: \mu_{`r most_2010_s`} = \mu_{`r most_2017_s`}$$ $$H_A: \mu_{`r most_2010_s`} \neq \mu_{`r most_2017_s`}$$
```{r}
t.test(most[,1],most[,2],var.equal = TRUE)
```

We fail to reject the null hypothesis at $\alpha=0.05$ and conclude that there is no difference in mean apprehensions between `r most_2010_s` in 2010 and `r most_2017_s` in 2017.

## Statistical Tests: Variance Test for Three-month Period {.smaller}
$$H_0: \sigma^2_{`r max_2010_period`} = \sigma^2_{`r max_2017_period`}$$ $$H_A: \sigma^2_{`r max_2010_period`} \neq \sigma^2_{`r max_2017_period`}$$

```{r}
var.test(max_three$max_2010,max_three$max_2017)
```

We fail to reject the null hypothesis at $\alpha=0.05$ and conclude that the variances of the three-month period `r max_2010_period` and of `r max_2017_period` are equal.

## Statistical Tests: Two Sample t-test for Three-month Period {.smaller}
$$H_0: \mu_{`r max_2010_period`} = \mu_{`r max_2017_period`}$$ $$H_A: \mu_{`r max_2010_period`} \neq \mu_{`r max_2017_period`}$$
```{r}
t.test(max_three$max_2010,max_three$max_2017,var.equal = TRUE)
```

We fail to reject the null hypothesis at $\alpha=0.05$ and conclude that there is no difference in mean apprehensions between the three-month period of `r max_2010_period` in 2010 and of `r max_2017_period` in 2017.

## Time Series {.smaller}
In order to explore the claim that US border apprehensions are at an all-time low when compared to 17 years ago, a time series plot was used to graph long-term trend.
```{r}
tsplot(ts)
```

## Conclusion {.smaller}
Through the use of bar plots and statistical tests, we see that the trend has not changed significantly from 2010 to 2017. However, after looking at the trend over 17 years, it is evident that there has been a downward decline in border apprehensions from 2000 to 2017 and that the number of apprehensions in 2017 is at indeed an all-time low.
